\bibliographystyle{humannat}
%\bibliography{references}

%\backmatter@sglvgdor

% Referencias
%https://www.overleaf.com/learn/latex/Bibliography_management_with_bibtex
\begin{thebibliography}{99}

\bibitem{vpn_comparison}
Abdulazeez, A., Salim, B., Zeebaree, D., y Doghramachi, D. (2020). Comparison of VPN Protocols at Network Layer Focusing on WireGuard Protocol. \textit{International Association of Online Engineering}. Recuperado de https://www.learntechlib.org/p/218341/

\bibitem{linux_network_admin}
Bautts, M., y Dawson, M. (2000). \textit{Linux Network Administrator’s Guide}. O’Reilly Media, 3ra edición.

\bibitem{linux_masquerade}
Bautts, M., y Dawson, M. (2000). \textit{Linux IP Masquerade HOWTO}. Disponible en: \url{https://tldp.org/HOWTO/IP-Masquerade-HOWTO/}

\bibitem{headscale}
Headscale. \textit{An Open Source, Self-Hosted Implementation of the Tailscale Control Server}. Disponible en: \url{https://github.com/juanfont/headscale}

\bibitem{computer_networking}
Kurose, J. F., y Ross, K. W. (2017). \textit{Computer Networking: A Top-Down Approach}. Pearson, 7ma edición.

\bibitem{linux_routing}
Linux Documentation Project. \textit{Linux Advanced Routing and Traffic Control HOWTO}. Disponible en: \url{https://tldp.org/HOWTO/Adv-Routing-HOWTO/}

\bibitem{vpn_protocols}
Narayan, S., Williams, C. J., Hart, D. K., y Qualtrough, M. W. (2015). Network performance comparison of VPN protocols on wired and wireless networks. \textit{2015 International Conference on Computer Communication and Informatics (ICCCI)}. doi:10.1109/iccci.2015.7218077

\bibitem{unix_philosophy}
Basics of the Unix Philosophy. Disponible en: \url{https://cscie2x.dce.harvard.edu/hw/ch01s06.html}

\bibitem{tailscale_derp}
Tailscale. \textit{Terminology and Concepts}. Disponible en: \url{https://tailscale.com/kb/1155/terminology-and-concepts#relay}

\bibitem{tailscale_ip_pool}
Tailscale. \textit{IP Pool}. Disponible en: \url{https://tailscale.com/kb/1304/ip-pool}

\bibitem{tailscale_nat}
Tailscale. \textit{Troubleshooting Device Connectivity}. Disponible en: \url{https://tailscale.com/kb/1411/device-connectivity#nat-types}

\bibitem{tailscale_overview}
Tailscale. \textit{What is Tailscale?} Disponible en: \url{https://tailscale.com/kb/1151/what-is-tailscale/}

\bibitem{nat_traversal}
Tailscale. \textit{How NAT Traversal Works}. Disponible en: \url{https://tailscale.com/blog/how-nat-traversal-works}

\bibitem{wireguard}
WireGuard. \textit{WireGuard: Fast, Modern, Secure VPN Tunnel}. Disponible en: \url{https://www.wireguard.com/}

\end{thebibliography}

